Leadership across cultures and contexts: an exploratory analysis

### 2020-05-06 leadership_across_cultures_contexts.Rmd
Added analysis of coercive authority. Working on Discussion section.

loadd(all_data)
loadd(all_data2)
loadd(all_study_vars)
loadd(df_func)
loadd(df_qual)
loadd(features)
loadd(feature_models)
loadd(follower_benefits_txt)
loadd(follower_costs_txt)
loadd(follower_benefits_cult)
loadd(follower_costs_cult)
loadd(functions_support_cult)
loadd(functions_support_txt)
loadd(highstatus_plot)
loadd(leader_benefits_txt)
loadd(leader_benefits_cult)
loadd(leader_costs_txt)
loadd(leader_costs_cult)
loadd(m_lpca_func)
loadd(m_lpca_qual)
loadd(m_pvclust_func)
loadd(m_pvclust_qual)
loadd(multi_aic)
loadd(multi_allvars)
# loadd(p_heatmap_groups)
# loadd(p_heatmap_region)
# loadd(p_heatmap_sex)
# loadd(p_heatmap_subsis)
loadd(p_heatmap_feature_subsis)
loadd(p_heatmap_feature_region)
loadd(p_heatmap_feature_sex)
loadd(p_heatmap_feature_groups)
loadd(plot_costs_benefits)
loadd(plot_func_qual)
loadd(plot_pubdate)
loadd(qualities_support_cult)
loadd(qualities_support_txt)

@@

```{r varsupportcb, echo=FALSE, warning=FALSE, message=F, fig.width=15, fig.height=11, fig.cap="Support for each coded variable for the costs and benefits of leadership and followership. Blue circles: percent of text records with evidence of support (95% CI computed with a binomial mixed effects models with random intercept for author nested within culture). Red triangles: percent of cultures with evidence of support (95% CI computed with a cluster bootstrap)."}
ggsave(file="Figures/variablecostsbenefits.pdf", plot_costs_benefits)
plot_costs_benefits
```

@@

## When do leaders also have high status?

@@

@@

@@

@@

```{r highstatusplot, echo=F, message=F, fig.width=8, fig.height=6, fig.align='center', fig.cap="Lasso logistic regression coefficients, which indicate the words whose frequencies in each text record best predicted evidence for the *high status* leader quality in each text record. Coefficients estimated with glmnet package using cross-validation to determine the optimal value of lambda [@friedman_regularization_2010]. Red values are positive predictors; purple values are negative predictors. X-axis is on a log 10 scale."}
highstatus_plot + scale_x_log10()
```

>>>>

loadd(all_data)
loadd(all_data2)
loadd(all_study_vars)
loadd(coercive_plot)
loadd(df_func)
loadd(df_qual)
loadd(features)
loadd(feature_models)
loadd(follower_benefits_txt)
loadd(follower_costs_txt)
loadd(follower_benefits_cult)
loadd(follower_costs_cult)
loadd(functions_support_cult)
loadd(functions_support_txt)
loadd(highstatus_plot)
loadd(leader_benefits_txt)
loadd(leader_benefits_cult)
loadd(leader_costs_txt)
loadd(leader_costs_cult)
loadd(m_lpca_func)
loadd(m_lpca_qual)
loadd(m_pvclust_func)
loadd(m_pvclust_qual)
loadd(multi_aic)
loadd(multi_allvars)
# loadd(p_heatmap_groups)
# loadd(p_heatmap_region)
# loadd(p_heatmap_sex)
# loadd(p_heatmap_subsis)
loadd(p_heatmap_feature_subsis)
loadd(p_heatmap_feature_region)
loadd(p_heatmap_feature_sex)
loadd(p_heatmap_feature_groups)
loadd(plot_costs_benefits)
loadd(plot_elastic_status)
loadd(plot_elastic_coercive)
loadd(plot_func_qual)
loadd(plot_pubdate)
loadd(qualities_support_cult)
loadd(qualities_support_txt)

@@

```{r varsupportcb, echo=FALSE, warning=FALSE, message=F, fig.width=15, fig.height=11, fig.cap="Support for each coded variable for the costs and benefits of leadership and followership. Blue: percent of text records with evidence of support (95% CI computed with a binomial mixed effects models with random intercept for author nested within culture). Red: percent of cultures with evidence of support (95% CI computed with a cluster bootstrap)."}
ggsave(file="Figures/variablecostsbenefits.pdf", plot_costs_benefits)
plot_costs_benefits
```

@@

## When do leaders have high status?

@@

To determine which leader qualities and functions were associated with evidence for high status, we fit a logistic elasticnet model of *High status* as a function of all quality and function variables, with the lasso penalty ($\alpha = 1$). The non-zero coefficients indicated that *Punishment* was a negative predictor, all other functions, including *Organize cooperation*, *Ritual functions*, and *Provide counsel/direction* were non-predictors, and *Wealthy*, *Strategic nepotism*, *Age*, *Experienced/accomplished*, and several others, were positive predictors. See Figure \@ref(fig:elastichighstatus).

```{r elastichighstatus, fig.width=10, fig.cap="Coefficients of logistic elasticnet regression models [@friedman_regularization_2010] of evidence for *High Status*. A: Coefficients indicate the words whose frequencies in each text record best predicted evidence for *High status* in each text record. B: Non-zero coefficients of all quality and function variables that best predicted evidence for *High status*. Both models used the lasso penality ($\\alpha=1$), with $\\lambda_{1se}$ chosen by cross-validation (1 SE from \\lambda_{min}). Red values are positive predictors; purple values are negative predictors. Coefficents = 0 not displayed. X-axes are odds ratios on a log 10 scale."}

highstatus_plot <- highstatus_plot + scale_x_log10()
highstatus_plot + plot_elastic_status + plot_annotation(title= "Predictors of High status", tag_levels = 'A', caption = 'Odds ratio', theme=theme(plot.caption=element_text(hjust=0.5, size=12, margin=margin(t=0))))
```

@@

## When do leaders have coercive authority?

```{r elasticcoercive, fig.width=10, fig.cap="Coefficients of logistic elasticnet regression models [@friedman_regularization_2010] of evidence for *Coercive authority*. A: Coefficients indicate the words whose frequencies in each text record best predicted evidence for *Coercive authority* in each text record ($\\alpha = 0.5$). B: Non-zero coefficients of all quality and function variables that best predicted evidence for *Coercive authority* ($\\alpha=1$). Both models chose $\\lambda_{1se}$ by cross-validation (1 SE from \\lambda_{min}). Red values are positive predictors; purple values are negative predictors. Coefficents = 0 not displayed. X-axes are odds ratios on a log 10 scale."}

coercive_plot_plot <- coercive_plot + scale_x_log10()
coercive_plot_plot + plot_elastic_coercive + plot_annotation(title= "Predictors of Coercive authority", tag_levels = 'A', caption = 'Odds ratio', theme=theme(plot.caption=element_text(hjust=0.5, size=12, margin=margin(t=0))))
```

@@

We found strong evidence that several dimensions of leadership were universal across cultures, and across group contexts within cultures. We found evidence that leaders function to resolve conflict, organization cooperation, and provide counsel and direction in over 70% of cultures, and are seen as high status, knowledgeable and intelligence, and experienced and accomplished in about 80% or more of cultures. See Figure \@ref(fig:varsupport). Leaders benefitted materially, reproductively, and socially in 50% or more of cultures. See Figure \@ref(varsupportcb). Some common leader dimensions also did not vary by continental region, subsistence strategy, group context, or leader sex. These included qualities, such as being knowledgeable and intelligence, wealthly, strategically nepotistic, and generous, and functions, such as resolving conflict and representing the group. These dimensions are therefore candidates for universal dimensions of human leadership. By "universal", we do not mean that all leaders have all these traits. Instead, we mean that these traits are found in some leaders across all cultures and contexts.

Many leadership dimensions did vary across cultures and contexts, however, including functions such as organizing cooperation, providing counsel and direction and prosocial investment, and qualities such as high status and aggressiveness. See Figure \@ref(fig:heatmapdrop1)

@@

```{r highstatusplot, echo=F, message=F, fig.width=8, fig.height=6, fig.align='center', fig.cap="Lasso logistic regression coefficients, which indicate the words whose frequencies in each text record best predicted evidence for the *high status* leader quality in each text record. Coefficients estimated with glmnet package using cross-validation to determine the optimal value of lambda [@friedman_regularization_2010]. Red values are positive predictors; purple values are negative predictors. X-axis is on a log 10 scale."}
# highstatus_plot + scale_x_log10()
```
